Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-21 paper.tex
Add explanation for non-horrible scaling of naive algorithm on depth benchmark

This setup is challenging for the incremental algorithm because (1) no rule is ever applied, so incrementality does not help; and (2) the incremental algorithm expends a non-negligible amount of effort for each of the $n$ hypotheses, whereas the naive algorithm can, at least for small $k$, decide fairly quickly that the rule is not applicable.
And indeed, Fig.~\ref{fig:erase-noprecomp} shows that while the naive approach slows down for greater $k$, big constant factors cause the incremental approach to remain slower for $k$ up to 5.

>>>>

This setup is challenging for the incremental algorithm because (1) no rule is ever applied, so incrementality does not help; and (2) the incremental algorithm expends a non-negligible amount of effort for each of the $n$ hypotheses, whereas the naive algorithm can, at least for small $k$, decide fairly quickly that the rule is not applicable.
And indeed, Fig.~\ref{fig:erase-noprecomp} shows that while the naive approach slows down for greater $k$ (though not by much since the context contains only $n = 6$ hypotheses), big constant factors cause the incremental approach to remain slower for $k$ up to 5.
